Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-28 document/ms.tex
some notes to self

\section{Separable Distribution}

>>>>

In practice, the variance of this approximation depends on the choice of
interim prior and, in particular, it is useful to include the completeness
function.
\dfmtodo{BLAH BLAH BLAH.}

\section{The completeness function \& dataset}

\dfmtodo{%
Describe Erik's data products and our model of the completeness in boxes
extended artificially beyond the original range.
Also describe the re-sampling procedure for the candidate parameters.
}

\section{Separable distribution}
